A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
better cart

    -M 5 -N 5 & 13.94 & 25.41 & 2m43.363s & 123 & 62 \\ \hline
    -M 5 -N 10 & 13.82 & 25.34 & 4m54.547s & 145 & 73 \\ \hline
    -M 5 -N 15 & 13.94 & 25.41 & 7m9.537s & 123 & 62 \\ \hline
    -M 5 -N 20 & 13.88 & 25.39 & 9m18.095s & 133 & 67 \\ \hline
  \end{tabular}
  \caption{Results for CART.}
  \label{tbl:results_cart}
  \end{center}
\end{table}

CART results are displayed in Table \ref{tbl:results_cart}.
From these results we can see that there isn't a lot of variation in the results.
The algorithm also performs badly when compared to C4.5 or ADTree.

>>>>

    -M 5 -N 5 & 13.94 & 25.41 & 2m43.363s & 123 & 62 \\ \hline
    -M 5 -N 10 & 13.82 & 25.34 & 4m54.547s & 145 & 73 \\ \hline
    -M 5 -N 15 & 13.94 & 25.41 & 7m9.537s & 123 & 62 \\ \hline
    -M 5 -N 20 & 13.88 & 25.39 & 9m18.095s & 133 & 67 \\ \hline
  \end{tabular}
  \caption{Results for CART with discretized data.}
  \label{tbl:results_cart_discr}
  \end{center}
\end{table}

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Parameters} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} & \textbf{Nodes} & \textbf{Leaves} \\ \hline
    -M 2 -N 5 & 12.68 & 22.26 & 2m34.703s & 157 & 79 \\ \hline
    -M 2 -N 10 & 12.72 & 22.26 & 4m49.261s & 151 & 76 \\ \hline
    -M 2 -N 15 & 12.22 & 21.34 & 7m4.560s & 237 & 119 \\ \hline
    -M 2 -N 20 & 11.75 & 21.70 & 9m14.989s & 341 & 171 \\ \hline

    -M 3 -N 5 & 12.68 & 22.26 & 2m21.439s & 157 & 79 \\ \hline
    -M 3 -N 10 & 12.72 & 22.26 & 4m35.048s & 151 & 76 \\ \hline
    -M 3 -N 15 & 12.22 & 21.34 & 6m45.982s & 237 & 119 \\ \hline
    -M 3 -N 20 & 11.84 & 21.70 & 7m44.483s & 321 & 161 \\ \hline

    -M 5 -N 5 & 12.72 & 22.26 & 2m18.255s & 151 & 76 \\ \hline
    -M 5 -N 10 & 12.60 & 22.78 & 4m28.169s & 171 & 86 \\ \hline
    -M 5 -N 15 & 13.29 & 22.01 & 6m45.657s & 83 & 42 \\ \hline
    -M 5 -N 20 & 12.22 & 21.43 & 8m53.232s & 259 & 130 \\ \hline
  \end{tabular}
  \caption{Results for CART with non-discretized data.}
  \label{tbl:results_cart_raw}
  \end{center}
\end{table}

CART results are displayed in tables \ref{tbl:results_cart_discr} and
\ref{tbl:results_cart_raw}.
From these results we can see that there isn't a lot of error rate variation
for each type of data.
The algorithm also performs worse compared to C4.5 or ADTree
and takes a much longer time to build the classifier.
